Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-17 main.tex
Updated my affiliation

% author names and IEEE memberships
\author{Marko~Ristic$^{1}$,
        Benjamin~Noack$^{2}$,~\IEEEmembership{Member,~IEEE,}
        and~Uwe~D.~Hanebeck$^{1}$,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
\thanks{$^{1}$Marko Ristic and Uwe D. Hanebeck are with the Intelligent Sensor-Actuator-Systems Laboratory (ISAS), Institute for Anthropomatics, Karlsruhe Institute of Technology (KIT), Germany (e-mail: \{marko.ristic, uwe.hanebeck\}@kit.edu).}% <-this % stops a space
\thanks{$^{2}$Benjamin Noack is with the Autonomous Multisensor Systems Group (AMS), Institute for Intelligent Cooperating Systems (ICS), Otto von Guericke University Magdeburg (OVGU), Germany (e-mail: benjamin.noack@ovgu.de).}}% <-this % stops a space

>>>>

% author names and IEEE memberships
\author{Marko~Ristic$^{1}$,
        Benjamin~Noack$^{1}$,~\IEEEmembership{Member,~IEEE,}
        and~Uwe~D.~Hanebeck$^{2}$,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
\thanks{$^{1}$Marko Ristic and Benjamin Noack are with the Autonomous Multisensor Systems Group (AMS), Institute for Intelligent Cooperating Systems (ICS), Otto von Guericke University Magdeburg (OVGU), Germany (e-mail: \{marko.ristic, benjamin.noack\}@ovgu.de).}% <-this % stops a space
\thanks{$^{2}$Uwe D. Hanebeck is with the Intelligent Sensor-Actuator-Systems Laboratory (ISAS), Institute for Anthropomatics, Karlsruhe Institute of Technology (KIT), Germany (e-mail: uwe.hanebeck@kit.edu).}}% <-this % stops a space
